---
title: "Markdown - STAT 6021 Project 1 Group 3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(MASS)
```


```{r, echo=FALSE}
#Read csv into data
data = read.csv(file = 'diamonds4.csv', header = T)
```


# Group Members: Mary Evanston, Brian Wickens, OC Ofoma, Catherine Bielick



# Executive Summary

Executive Summary text here.  
use two spaces after end of previous line to create a new line.





# Dataset and Variable Description

This dataset includes the parameters carat, clarity, color, cut, and prices for 1,214 diamonds available for purchase on bluenile.com.  

### Carat
description

### Clarity
description

### Color
description

### Cut
description

### Price
Cost of each diamond in USD. Unless otherwise specified, price will be considered the response variable in this analysis.



# Visualizations and Commentary



```{r}
ggplot(data, aes(x = carat, y = price)) +
  geom_point() +
  labs() +
  ggtitle("Title")
```

```{r}
ggplot(data, aes(x = clarity, y = price)) +
  geom_point() +
  labs() +
  ggtitle("Title")
```








# Regression Analysis

```{r}
#Multiple Linear regression of price vs carat

reg1 = lm(price ~ carat, data = data)

ggplot(data = NULL, mapping = aes(x = reg1$model$carat , y = reg1$residuals)) +
  geom_point() +
  labs(x = 'Carat', y = 'Residuals') +
  geom_hline(yintercept = 0) +
  ggtitle('Residual Plot of Untransformed Price ~ Carat SLR')

#Boxcox for transformation
boxcox(reg1, lambda = seq(0.25, 0.4, by = 0.05))
```

```{r}
data$price.x = data$price^0.31

#Regression with lambda power transformation on price response variable
reg2 = lm(price.x ~ carat, data = data)

ggplot(data, aes(x = carat , y = reg2$fitted.values)) +
  geom_point() +
  labs(x = 'Carat', y = 'Price (Transformed)')
```










